---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
library(dplyr)
library(car)
```

```{r}
data <- read.csv('../data/insurance.csv')
head(data)
```
We will check whether the number of children affects the insurance fee or not.

```{r}
# get columns "children" and "charges"
data <- data[,c(4, 7)]
head(data)
```

```{r}
unique(data$children)
```

The number of children in a family can take values from 0 to 5

```{r}
boxplot(data$charges ~ data$children)
means <- tapply(data$charges, data$children, mean)
points(means, pch=20)
```

In all groups of "children", appear outliers in charges
We can see that there is the slightly difference in charge's mean between groups

```{r}
data %>% group_by(children)  %>%
                    summarise(mean_charge = mean(charges))
```



```{r}
data$children <- as.factor(data$children)
lm1 <- lm(charges~children, data=data) 
anova(lm1)
```

anova test with linear model:\
Hypotheisis:\
H0: The mean between groups is the same\
H1: At least 1 couple of group has difference mean\

Choose anpha=0.05, because p-value < 0.05, we reject H0 and accept H1

```{r}
summary(lm1)
```

Paired mean comparison:

```{r}
aov1 <- aov(charges~children, data=data) 
summary(aov1)
```

```{r}
#test all possible comparisons of two means. 
with(data, pairwise.t.test(charges, children, p.adj = "bonferroni"))
```
As the bellow matrix, because p-value is more than 0.05 in all couple, we can conclusion that the number of children don't affect to insurance fee.

