---
title: "R Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r}
library(faraway)
```

# 1. Data "rats"

```{r}
data("rats")
```

```{r}
head(rats)
```

```{r}
# multiply model:
rats_int <- aov(time~poison*treat, data=rats)
summary(rats_int)
```
With hypothesis:\
H0: There is no interaction between poison and treat that can affect the time\
H1: The interaction between poison and treat can affect the time.\
choose anpha = 0.05, p-value = 0.112 > 0.05 so we can not reject H0, we accept that there is no interaction between poison and treat that can affect the time.\
Therefore, we will use add model instead of multiply model

```{r}
# add model:
rats_add <- aov(time ~ poison + treat, data = rats)
summary(rats_add)
```
Hypothesis for poison:\
H0: for each i, all anpha i equal to 0\
H1: exist i that anpha i != 0\
Hypothesis for treat:\
H0: for each j, all beta j equal to 0\
H1: exist j that anpha j != 0\

The result of aov function show that both poison and treat affects to time (p-value <= 0.05)

```{r}
TukeyHSD(rats_add) # test for the interaction between difference groups inside each variable
```

```{r}
# shapiro test for residual
shapiro.test(residuals(rats_add))
```
# 2. Data "warpbreaks"

```{r}
# bộ dữ liệu mới
data("warpbreaks")
head(warpbreaks)
```


```{r}
str(warpbreaks)
```

```{r}
with(warpbreaks, interaction.plot(wool, tension, breaks, lwd=2, col=2:4))
```

```{r}
with(warpbreaks, interaction.plot(wool, tension, breaks, lwd=2, col=2:3))
```

```{r}
summary(aov(breaks~wool*tension, data=warpbreaks))
```

If we choose anpha = 0.06, wool affects to breaks. If we choose anpha = 5%, it dose not affect.\
Choose the anpha=0.05, tension impact breaks, wool and tension have interaction.


```{r}
war_model <- aov(breaks~wool*tension, data=warpbreaks)
```

```{r}
TukeyHSD(war_model)
```


```{r}
shapiro.test(residuals(war_model))
```



